Equilibria and Convergence of Fictitious Play on Network Aggregative Games

### 2021-05-26 Documents/FP in NAGs/neurips_2021.tex
Update neurips_2021.tex
Updated Section 4

>>>>

	We note at this point that a related result was found in \cite{Ewerhart2020}. In particular, the authors showed that, when playing on a zero-sum network game, agents learning through Fictitious Play achieve non-positive regret, regardless of the behaviour of the other agents. This is a slightly stronger condition than the CCE, in which agents achieve non-positive regret if all other agents do not deviate from the distribution $\mathcal{D}$. However, the result in \cite{Ewerhart2020} applies only under the zero-sum condition, whereas Theorem \ref{thm::NACTFPtoCCE} applies in all NA games.
